Local metal-insulator transition in a generalised Anderson impurity model

### 2022-05-31 gen-siam-manuscript/gen-siam.tex
Added abstract

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
\end{abstract}

>>>>

\begin{abstract}
We propose a minimal impurity model as the auxiliary model that can be used to study metal-insulator transitions in bulk models like the Hubbard. The minimal model is obtained by adding spin-exchange physics and local bath correlation into the single impurity Anderson model. We prove this by demonstrating the presence of both metallic (screened) as well as insulating (unscreened) phases through a renormalisation group treatment of such a model. We show that this impurity phase transition is brought about by increased charge isospin fluctuations in the bath; indeed, it is these fluctuations that destabilise the Kondo cloud and lead to a breakdown of screening. This transition is characterised by a measure of many-particle entanglement \(\left(\chi\right)\) which acts as an order parameter - it is non-zero in the screened phase and reduces to zero in the unscreened phase. This is made possible by relating the impurity Greens function to \(\chi\), and it turns out that such relations exist for any 1-particle or 2-particle impurity-bath correlation. Such an auxiliary model approach to studying bulk systems of strong correlation is qualitatively different from a more conventional approach like dynamical mean-field theory or its cluster variants. There is no need to obtain the impurity model self-consistently, and this makes it possible to directly relate the thermodynamics of the bulk model to that of the impurity.
\end{abstract}
